---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
# This chunk hides all code and messages from the final report
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
```

```{r}
library(tidyverse)
file <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vSCRRgi6Q17MhD6IwXig45hpsqKX1SBVGF_zf_DgMDBoPceAOy1wA7RSUyT0DoYFy738ijvodND-ESu/pub?output=csv"
logged_data <- read_csv(file)
  
latest_data <- logged_data %>%
  rename(
    timestamp = 1,
    device = 2,
    items = 3,
    headphones = 4,
    environment = 5
  ) %>%
  mutate(
    device = str_remove(device, " \\(.*\\)"),
    headphones = str_remove(headphones, " \\(.*\\)"),
    environment = str_remove(environment, " \\(.*\\)")
  )

total_obs <- nrow(latest_data) 
avg_items <- round(mean(latest_data$items, na.rm = TRUE), 2)
```

```{css}
body {
  font-family: sans-serif;
  color: #333;
  line-height: 1.5;
}

h2 {
  color: #2c3e50;
  border-bottom: 1px solid #ccc;
}
```

## Exploring Student Study Desk Habits

This report analyzes how students at the University of Auckland set up their workspaces. I am looking at what devices they use and how many physical items (like books and pens) they keep on their desks.

### Workspace Observations

The bar charts below show the most popular devices used for studying and the different types of environments where I collected my data.

```{r chart1}
# Creating a bar chart for the devices used
ggplot(latest_data, aes(x = device)) + 
  geom_bar(fill = "steelblue") +
  labs(title = "Count of Primary Study Devices", 
       x = "Device Type", 
       y = "Frequency")
```

```{r chart2}
# Creating a bar chart for the study environments
ggplot(latest_data, aes(x = environment)) + 
  geom_bar(fill = "darkseagreen") +
  labs(title = "Distribution of Study Environments", 
       x = "Environment", 
       y = "Count")
```

### Summary of Data

I have collected a total of **`r total_obs`** observations from across the campus. On average, I found that students have **`r avg_items`** non-electronic items on their desks while they work.

This information helps us understand how students organize their physical space depending on the technology they are using.

